Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-07 draft.tex
changes to tables and explanations of columns

\def\Title{
	Creating More Meaningful Explanations of Audio Deepfake Detection
	\newline\newline
	Explaining Audio Deepfake Detection with Perceptible Features and LIME
	\newline\newline
	Understandable Explanations of Synthetic Voice Detection with Perceptible Features and LIME
}
\def\Subtitle{}

@@

@@

	Li et al. \cite{li_comparative_2022} also approach
	perceptible features in their work, combining them with imperceptible (referred to as physical
	in the work) features and using various neural networks in their experiments. Overall, the
	combination of perceptible and imperceptible features was able to produce the best performance
	results of the experiments, which were performed as well on the dataset of the ASV2022
	Challenge \cite{yi_add_2024}.

@@

			defined as follows:

@@

			basis, which we will further refer to as trust. The trust per feature can be defined as

@@

			\centering\tiny

@@

				Simple & standard & until 3474 & 95.02\% & 0.03702 & 0.90297 \\
				3 hidden layers & standard & until 10000 & 96.27\% & 0.03214 & 0.81763 \\
				Simple & standard & until 23833 2 epochs & 90.07\% & 0.90069 & 0.78889 \\
				Simple & standard & until 10000 2 epochs & 94.43\% & 0.04408 & 0.89445 \\
				Simple & standard & until 10000 & 94.28\% & 0.04840 & 0.90182 \\
				3 convolutional layers & standard & until 10000 & 62.80\% & 0.37198 & 0.50051 \\
				Simple & expand pitch\-flucs & until 10000 & 93.31\% & 0.05661 & 0.92727 \\
				3 hidden layers & expand pitch\-flucs & until 10000 & 93.87\% & 0.05317 & 0.83263

@@

			\caption{ROC curve of the best-performing model, with 3 hidden layers in the terminus and that standard feature set.}

@@

			\caption{ROC curve of the model with expanded pitch fluctuation features and a terminus with three hidden layers.}

@@

		\ref{table:eval-results}. The model that achieved the best results was trained on the
		first 10000 samples of the dataset and evaluated on the rest evaluated using the methods
		previously described. It has an evaluation accuracy of 96.3\% with the default threshold of
		0.5, with an EER of approximately 0.03214. This outperforms other results tested in the

>>>>

\def\Title{Explaining Audio Deepfake Detection with Perceptible Features and LIME}
\def\Subtitle{}

@@

\makeatletter
\newcommand\notsotiny{\@setfontsize\notsotiny\@vipt\@viipt}
\makeatother

@@

	Li et al. \cite{li_comparative_2022} also approach perceptible features in their work,
	combining them with imperceptible (referred to as physical in the work) features and using
	various neural networks in their experiments. Overall, the combination of perceptible and
	imperceptible features was able to produce the best performance results of the experiments,
	which were performed as well on the dataset of the ASV2022 Challenge \cite{yi_add_2024}.

@@

			defined as follows for every \(f \in F\):

@@

			basis, which we will further refer to as trust. The trust per feature \(f \in F\) can
			be defined as follows:

@@

			\centering\notsotiny

@@

				Simple & standard & 3474 & 95.02\% & 0.03702 & 0.90297 \\
				3 hidden layers & standard & 10000 & 96.27\% & 0.03214 & 0.81763 \\
				Simple & standard & 23833 2 epochs & 90.07\% & 0.90069 & 0.78889 \\
				Simple & standard & 10000 2 epochs & 94.43\% & 0.04408 & 0.89445 \\
				Simple & standard & 10000 & 94.28\% & 0.04840 & 0.90182 \\
				3 convolutional layers & standard & 10000 & 62.80\% & 0.37198 & 0.50051 \\
				Simple & expand pitch\-flucs & 10000 & 93.31\% & 0.05661 & 0.92727 \\
				3 hidden layers & expand pitch\-flucs & 10000 & 93.87\% & 0.05317 & 0.83263

@@

			\caption{ROC curve of the best-performing model, with 3 hidden layers in the terminus
			and that standard feature set.}

@@

			\caption{ROC curve of the model with expanded pitch fluctuation features and a
			terminus with three hidden layers.}

@@

		\ref{table:eval-results}. The table covers the type of terminus model used, where a
		"simple" terminus model does not include hidden layers, the set of features used, where
		"standard" is the feature set as described above, with expanded pitch fluctuations being
		the same feature set with the addition of pitch fluctuation features with different
		comparison distances, the training batch size and the number of epochs per batch if there
		were more than one, followed by several metrics for comparison. Figures
		\ref{fig:roc_cterm}, \ref{fig:roc_mpf} and \ref{fig:roc_mpf_cterm} depict the ROC curve of
		three of the models, which were selected for use in explanation generation in the
		following section.
		The model that achieved the best results was trained on the first
		10000 samples of the dataset and evaluated on the rest evaluated using the methods
		previously described. It has an evaluation accuracy of 96.3\% with the default threshold
		of 0.5, with an EER of approximately 0.03214. This outperforms other results tested in the
